Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-12-16 WSSSPE4_report/wg_best_practices_undergrads.tex

\begin{enumerate}
\item Create channels of communication including a mailing list, a
  slack channel, and a git repository
\item Review literature on best and good-enough practices for
  scientific computing as well as literature on pedagogy for
  scientific and research computing
\item Organize a telecon to organize a workshop to write the
  curriculum and decide how to bring in outside experts
\item Write a draft of the curriculum
\item Invite the broader community to contribute to a more complete
  curriculum
\end{enumerate}

>>>>

\begin{enumerate}
\item Create channels of communication including a mailing list, a
  slack channel, and a git repository (done)
\item Review literature on best and good-enough practices for
  scientific computing as well as literature on pedagogy for
  scientific and research computing (by February 1, 2017)
\item Organize a telecon to organize a workshop to write the
  curriculum and decide how to bring in outside experts (by February 1,
  2017)
\item Write a draft of the curriculum (by April 1, 2017)
\item Invite the broader community to contribute to a more complete
  curriculum (by April 30, 2017)
\end{enumerate}
